A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-09-19 journal/experiments.tex
initial work

\begin{figure}
    \centering
        \includegraphics[width=1.0\textwidth]{jscurve}
        \caption{Discovery curves for SpiderMonkey 1.6 faults}
        \label{jscurves}
 \end{figure}%
    ~ 
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{gcccurve}
        \caption{Discovery curves for GCC 4.3.0 wrong-code faults}
        \label{gcccurves}
    \caption{Discovery curves compared to best curves from Chen et. al PLDI 2013 data (FPF benchmark)}
\end{figure}

@@

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column is a fault ID. The next three columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization.  MUSEUM uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that ``fix'' a failure but also break some passing test(s), is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.

>>>>

\begin{figure}
    \centering
        \includegraphics[width=1.0\textwidth]{jscurve}
        \caption{Discovery curves for SpiderMonkey 1.6 faults}
        \label{jscurves}
 \end{figure}%
    ~ 
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{gcccurve}
        \caption{Discovery curves for GCC 4.3.0 wrong-code faults}
        \label{gcccurves}
    %\caption{Discovery curves compared to best curves from Chen et. al PLDI 2013 data (FPF benchmark)}
\end{figure}

@@

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column is a fault ID. The next three columns show localization rankings.  A ranking of 1 means that a code location \emph{in} the faulty code was presented to the user as the most likely location of the fault by the methodxs.  A ranking of, e.g., 22 however, would mean that a user examining code locations proposed as faulty by the method would not reach any faulty code until examining the 22nd such location proposed by the method.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization.  MUSEUM uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that ``fix'' a failure but also break some passing test(s), is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.
